Meta-analytic approaches and new effect sizes for treatment effects in comparative physiology

### 2021-05-17 MS/ms.Rmd
Small changes

#### *Literature Search and Data Collection*
To understand meta-analytic practices in comparative physiology, we searched for meta-analyses tackling comparative physiological questions that relied on data compiled from studies using animal model systems with more than a single species. All searches were conducted......**write details here**.

@@

#### *Multi-level Meta-Analysis when the Overall Effect is of Interest*
#### *Heterogenity Analysis: How Much Effect Size Variation Actually Exists?*
#### *Multi-level Metaregression to Understand Variation and Imrpove Interpretation*

@@

Quantifying effect size heterogenity (i.e., effect size variance) provides a pathway to explore hypotheses thought to explain why effect might vary across studies.

>>>>

#### *Literature Search and Survey Data Collection*
To understand meta-analytic practices in comparative physiology, we searched for meta-analyses tackling comparative physiological questions that relied on data compiled from studies using animal model systems with more than a single species. All searches were conducted......**write details here**.

@@

#### *Multi-level Meta-Analysis when the Overall Effect is of Interest*
#### *Heterogenity Analysis: How Much Effect Size Variation Actually Exists?*
Quantifying effect size heterogenity (i.e., effect size variance) provides a pathway to explore hypotheses thought to explain why effect might vary across studies.

#### *Multi-level Metaregression to Understand Variation and Imrpove Interpretation*

@@
